### 2014-08-31 LaTeX/RhodiumTheory.tex
A little bit on Mexico added.

These hypotheses do not seem unknown to armed actors.  The guerilla group Fuerzas Armadas Revolucionarios de Colombia (FARC) appears to have internalized these mechanisms.  In 1998 and 1999, the organization moved its violent operations from mostly rural areas of Colombia into major cities and near to the capital (Petras and Brescia 2000).  This coincided with economic strain caused by the implementation of an IMF/World Bank structural readjustment program.  However, the timing was likely not coincidental.  FARC advocates a number of political and economic reforms and chooses targets strategically related to these objectives.

@@

While FARC seems to exploit its ability to target areas of economic importance including cities, other insurgencies tend to be more peripheral.  India, for instance, has faced challenges by armed groups in its north-east for half a century.  However, this area of India is remote, primarily agrarian, and relatively less populous than other parts of India.  Indeed, for much of this period, India has experienced relatively robust economic growth.

>>>>

This hypothesis does not seem unknown to armed actors.  The guerilla group Fuerzas Armadas Revolucionarios de Colombia (FARC) appears to have internalized these mechanisms.  In 1998 and 1999, the organization moved its violent operations from mostly rural areas of Colombia into major cities and near to the capital (Petras and Brescia 2000).  This coincided with economic strain caused by the implementation of an IMF/World Bank structural readjustment program.  However, the timing was likely not coincidental.  FARC advocates a number of political and economic reforms and chooses targets strategically related to these objectives.

@@

While FARC seems to exploit its ability to target areas of economic importance including cities, other insurgencies tend to be more peripheral.  India, for instance, has faced challenges by armed groups in its north-east for half a century.  However, this area of India is remote, primarily agrarian, and relatively less populous than other parts of India.  Indeed, for much of this period, India has experienced relatively robust economic growth.  Mexico, now nearly a decade into a violent and complicated conflict between several organized criminal enterprises and the federal government, has maintained healthy economic performance.  For much of this time, the cartel violence generally occurred in rural areas along drug trafficking routes and not within major cities. \cite{beittel:2011} writes in 2011 that ``drug trafficking-related killings remain concentrated in a relatively few cities,'' but notes that the violence was beginning to expand in geographic range by 2010.
